Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-04-17 paper.tex
Clarify tows for odd speeds
Describe spectra plots

Approximately 1500 tows were performed, each one used for a single data point on
either a performance curve or wake map. A performance curve consisted of 31
tows, where during each tow the mean turbine tip speed ratio was held constant,
ranging from 0.1--3.1 in 0.1 increments. Full performance curve data were
acquired for tow speeds from 0.4 to 1.2 m/s in 0.2 m/s increments, for which
turbine diameter and approximate blade chord Reynolds number are presented in
Table~\ref{tab:Re}. Performance was also measured for $\lambda=1.9$ at tow
speeds $[0.3, 0.5, 0.7, 0.9, 1.1, 1.3]$ m/s, each of which consisted of two tows.

@@

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/wake_spectra}
\caption{Wake spectra at $z/H=0.25$, $y/R=-1.0$ (a) and $y/R=1.5$ (b). Dashed vertical
lines indicate $[1, 3, 6, 9]$ times the turbine rotational frequency.}
\label{fig:wake-spectra}
\end{figure}

>>>>

Approximately 1500 tows were performed, each one used for a single data point on
either a performance curve or wake map. A performance curve consisted of 31
tows, where during each tow the mean turbine tip speed ratio was held constant,
ranging from 0.1--3.1 in 0.1 increments. Full performance curve data were
acquired for tow speeds from 0.4 to 1.2 m/s in 0.2 m/s increments, for which
turbine diameter and approximate blade chord Reynolds number are presented in
Table~\ref{tab:Re}. Performance was also measured for $\lambda=1.9$ at tow
speeds $[0.3, 0.5, 0.7, 0.9, 1.1, 1.3]$ m/s for two tows each.

@@

Spectra of the cross-stream velocity normalized by the free stream are plotted
in Figure~\ref{fig:wake-spectra} for regions on either side of the turbine. On
the $-y$ side of the turbine there is broadband turbulence produced by blade
stall, and on the $+y$ side there is a clear peak in the spectra caused by the
blade passage. We see that on both sides there is higher spectral energy at
lower Reynolds numbers. On the $+y$ side of the turbine we notice higher
spectral energy at the blade passage frequency's first harmonic, or $6
f_\mathrm{turbine}$.

@@

\todo[inline]{Make sure the spectra are not just shifting due to normalizing the
noise.}

\begin{figure}[ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/wake_spectra}
\caption{Cross-stream velocity (normalized by $U_\infty$) spectra at $z/H=0.25$, 
$y/R=-1.0$ (a) and $y/R=1.5$ (b). Dashed vertical
lines indicate $[1, 3, 6, 9]$ times the turbine rotational frequency.}
\label{fig:wake-spectra}
\end{figure}
